SunPy - Python for Solar Physics

### 2014-01-31 2-2-Lightcurve.tex
edits to remaining sections

Time series data and their analyses are a fundamental part of solar
physics for which many data sources are available.
SunPy provides a \texttt{LightCurve} class
with a convenient and consistent interface for handling solar time-series
data.  The main engine behind the \texttt{LightCurve} class is
the {\texttt{pandas}} data-analysis library, and 
\texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
object. The \texttt{pandas} library contains a large amount
of functionality for manipulating and analysing time-series data,
making it an ideal basis for \texttt{LightCurve} \citep{mckinney2012}.  \texttt{LightCurve}
assumes that the input data are time-ordered list(s) of numbers, and each
list becomes a column in the \texttt{pandas} DataFrame object.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method.}
\label{code:goes_lc}
\end{listing}

Alternatively, if the data file already exists on the local system, the 
\texttt{LightCurve} object may instead be initialised using that file as input.
Once the \texttt{LightCurve} object has been created, it may be manipulated in 
a variety of ways in order to perform time-series analysis.

>>>>

Time series data and their analyses are a fundamental part of solar
physics for which many data sources are available.
SunPy provides a \texttt{LightCurve} class
with a convenient and consistent interface for handling solar time-series
data.  The main engine behind the \texttt{LightCurve} class is
the {\texttt{pandas}} data-analysis library.  
\texttt{LightCurve}'s \texttt{data} attribute is a \texttt{pandas.DataFrame} 
object. The \texttt{pandas} library contains a large amount
of functionality for manipulating and analysing time-series data,
making it an ideal basis for \texttt{LightCurve} \citep{mckinney2012}.  \texttt{LightCurve}
assumes that the input data are time-ordered list(s) of numbers, and each
list becomes a column in the \texttt{pandas} DataFrame object.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
>>> print goes.data['B_FLUX'].max()
2.55542e-05
>>> print goes.data['B_FLUX'].idxmax()
2011-06-07 06:41:26
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method. The maximum flux value in the GOES 1.0 - 8.0$\AA$\ channel 
is then retrieved along with the location in time of the maximum.}
\label{code:goes_lc}
\end{listing}

Alternatively, if the data file already exists on the local system, the 
\texttt{LightCurve} object may be initialised using that file as input.
%Once the \texttt{LightCurve} object has been created, it may be manipulated in 
%a variety of ways in order to perform time-series analysis.

### 2014-01-31 acknowledgements.tex
edits to remaining sections

\section{Acknowledgements}
Many of the larger features in SunPy have been developed with external support. 
Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
Summer of Code In Space (SOCIS) program, as well as prototyped GUI and 
N-Dimensional datatype implementations. In 2013, with support from Google's 
Summer Of Code (GSOC) program, through the Python Software Foundation, the 
\texttt{helio}, \texttt{hek2vso}, and \texttt{database} subpackages were 
developed. The Spectra and Spectrogram classes were implemented with support 
from the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
2012.

>>>>

\section{Acknowledgements}
Many of the larger features in SunPy have been developed with the generous support of 
external organizations. 
Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
Summer of Code In Space (SOCIS) program, as well as a prototype GUI and 
N-Dimensional datatype implementations. In 2013, with support from Google's 
Summer Of Code (GSOC) program, through the Python Software Foundation, the 
\texttt{helio}, \texttt{hek2vso}, and \texttt{database} subpackages were 
developed. The Spectra and Spectrogram classes were implemented with support 
from the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
2012.
